\section{Related Work}

\paragraph{Label imputation in EHRs.}
Missing labels in clinical datasets are rarely missing at random; their absence reflects institutional silos~\cite{ross_accuracy_2020} and clinical workflow patterns~\cite{li_imputation_2021}. Most imputation work targets missing continuous \textit{features} (vital signs, laboratory values)~\cite{psychogyios_missing_2023}, but imputing missing \textit{labels} is a distinct problem. The SickKids noise structure fits the Positive-Unlabeled (PU) learning paradigm~\cite{bekker_learning_2020}: positive labels are trustworthy, while the unlabeled class conflates true negatives with unobserved external events. Prior PU approaches treat the unlabeled class as a statistical quantity to estimate, whether through Bayesian mixture models~\cite{wang_bayesian_2023} or label-recovery frameworks for clinical codes~\cite{kumar_detecting_2025}. Our approach resolves the ambiguity directly: we query a validated Knowledge Graph against each patient's post-assessment diagnosis before training begins, converting a probabilistic inference problem into a clinical evidence lookup where the graph permits it.

\paragraph{Knowledge graphs and LLMs in clinical decision support.}
LLMs show strong capacity for medical knowledge imputation~\cite{yao_llm_imputation_2025} and clinical entity recognition from unstructured notes~\cite{islam_llm-based_2025}, but standalone LLM outputs lack auditability and hallucinate in high-stakes settings. Retrieval-augmented generation (RAG) over clinical guidelines improves extraction accuracy by grounding outputs in validated sources~\cite{li_automated_2024, nanua_retrieval-augmented_2025}. GraphRAG architectures~\cite{edge_local_2024, peng_graphrag_survey_2024} extend this by combining structured Knowledge Graph reasoning with contextual retrieval, enabling semantically coherent inference across interconnected clinical concepts. We adopt a GraphRAG architecture but depart from existing work in three ways: the Knowledge Graph is constructed dynamically from live clinical guidelines, enriched with ontology-standardized codes and quantitative literature evidence, and every diagnosis-to-test pathway is validated through a multi-agent clinical audit before use.

\paragraph{Meta-learning for noisy labels.}
Early approaches to learning with noisy labels modified the loss function itself. Loss-correction methods estimate a class-conditional noise transition matrix and use it to adjust either the loss or the model's predictions, yielding an unbiased estimator of the clean risk under ideal conditions~\cite{patrini_making_2017}. Generalized Cross Entropy~\cite{zhang_generalized_2018} and Symmetric Cross Entropy~\cite{wang_symmetric_2019} avoid explicit matrix estimation by interpolating between noise-tolerant and optimization-friendly loss families. These methods improve robustness when corruption follows class-level flip rates, but they impose a fixed rule at the loss level and cannot adapt per-sample trust as training progresses.

Sample selection methods addressed this limitation by choosing which examples to learn from at each step. MentorNet~\cite{jiang_mentornet_2018} learns a data-driven curriculum through an auxiliary network, typically requiring clean supervision to train the mentor. Co-teaching~\cite{han_coteaching_2018} removes the clean-data assumption by training two peer networks that exchange small-loss examples, at roughly twice the backbone cost. DivideMix~\cite{li_dividemix_2020} extends this idea by fitting a two-component Gaussian mixture to per-sample losses and recasting suspected-noisy examples as unlabeled data for semi-supervised co-training. These methods exploit the empirical finding that deep networks fit clean patterns before memorizing noise, but low loss is an imperfect proxy for label correctness. Under asymmetric corruption, genuinely difficult examples can resemble mislabeled ones, and the heuristic breaks down.

Meta-learning reweighting made the selection rule itself learnable through bilevel optimization. Learning to Reweight Examples (L2RW)~\cite{ren_learning_2018} optimizes one scalar weight per training example in each mini-batch to minimize loss on a small clean validation set, at roughly three times standard training cost. Meta-Weight-Net~\cite{shu_meta-weight-net_2019} replaces per-example weights with a small multilayer perceptron that maps loss to weight, but retains the clean-validation-set requirement. Confident Learning~\cite{northcutt_confident_learning_2019} takes a complementary approach, estimating the joint distribution of noisy and true labels to prune errors before training rather than reweight during it. LiLAW~\cite{moturu_lilaw_2025} compresses the meta-learner to three global scalar parameters ($\alpha$, $\beta$, $\delta$) that weight easy, moderate, and hard samples based on softmax agreement and prediction confidence. It retains bilevel updates against validation mini-batches but does not require those labels to be clean or unbiased, and adds no auxiliary networks. These properties match the SickKids setting, where a small trustworthy validation set may not exist and the noise structure (unrecorded external tests producing false negatives, not symmetric random flips) differs from the corruption patterns most benchmark methods were designed for.
