\section{Methods}

\subsection{Label imputation via Knowledge Graph}

The label imputation pipeline constructs an evidence-grounded Knowledge Graph (KG) mapping ICD-10 diagnosis codes to clinically indicated diagnostic tests. The KG serves as audited clinical ground truth: when a patient's post-assessment diagnosis maps to a test but the encounter lacks a positive label for that test, the label is imputed positive. Imputation runs offline over the training set only. No diagnosis codes are available at inference time.

\paragraph{Knowledge Graph construction.}
The graph is built in four stages.

\textit{Stage 1: Baseline rule generation.} GPT-5-mini generates triage rules mapping clinical observations to conditions and their required tests. To reduce hallucination, the model is grounded via RAG over the EPFL clinical guidelines dataset, with retrieved guideline texts providing in-context evidence.

\textit{Stage 2: Ontology standardization.} All entities are mapped to recognized medical ontologies through external APIs. Symptom nodes receive Human Phenotype Ontology (HP) and MONDO terms (EMBL-EBI OLS4 API); condition nodes are annotated with WHO ICD-10 codes (UMLS REST API) and ICD-10-CA codes (Canada Health Infoway FHIR); diagnostic test nodes receive LOINC panel codes.

\textit{Stage 3: Evidence enrichment.} Edges are weighted with quantitative literature evidence. Peer-reviewed article and patent co-occurrence counts (Europe PMC API) attach to symptom-to-condition and condition-to-test edges; clinical trial counts (ClinicalTrials.gov) attach to treatment pathways. This allows the system to distinguish well-supported clinical associations from marginal correlations.

\textit{Stage 4: Ontological expansion.} The graph is extended by integrating ClinGraph~\cite{johnson_clinvec_2024}, a 153K-node, ${\sim}$3M-edge clinical knowledge graph spanning SNOMED CT, ICD-10-CM, LOINC, RxNorm, and related vocabularies. ClinGraph back-fills missing cross-vocabulary codes and adds up to 500 first-degree neighbor nodes per existing node.

\paragraph{Multi-agent audit.}
Before imputation, every diagnosis-to-test pathway is validated by a four-persona multi-agent audit pipeline. The unit of review is a clinical triad: a (finding $\to$ condition $\to$ test) path extracted by traversing \texttt{INDICATES\_CONDITION} followed by \texttt{REQUIRES\_TEST} edges. Triads are deduplicated and sorted by clinical acuity (HIGH, MODERATE, STANDARD) to prioritize time-sensitive pathways.

Three independent personas evaluate each triad: a Protocol \& Triage Enforcer with RAG access over clinical guidelines, a Rapid Diagnostics Researcher querying live literature databases (Semantic Scholar, Europe PMC), and an ED Attending evaluating clinical flow pragmatics and never-event mitigation. A fourth persona, the ED Medical Director, synthesizes these assessments into a verdict (\textit{Verified}, \textit{Flagged for Review}, or \textit{Rejected}) and a continuous confidence score in $[0, 1]$. Three hard-flag conditions bypass scoring and unconditionally produce a \textit{Flagged} verdict: a genuine clinical error in the pathway, a Choosing Wisely flag, or zero guideline and literature support. Audit outcomes are written back as edge attributes and inform retrieval during imputation.

\paragraph{Imputation strategies.}
We evaluate two retrieval strategies. \textit{KG String Matching} uses bidirectional substring matching to map patient diagnosis strings to KG nodes, then traverses 1-hop (\texttt{REQUIRES\_TEST} or \texttt{DIRECTLY\_INDICATES\_TEST}) and 2-hop (\texttt{INDICATES\_CONDITION} $\to$ \texttt{REQUIRES\_TEST}) edges to identify indicated tests. A minimum-node threshold $\tau$ requires at least $\tau$ independently matched nodes to nominate a test before imputation, reducing false positives from broad symptom matches. \textit{GraphRAG Semantic Retrieval} embeds KG nodes and patient diagnoses using the MedEmbed biomedical language model, querying a local ChromaDB vector store to capture cases without lexical overlap. A sliding-window negation filter discards matches where the clinical concept is negated in the source text (e.g., ``no chest pain'' does not trigger ECG imputation). Indicated tests are ranked by aggregate cosine similarity across matched nodes and filtered by a threshold $\theta$.

\subsection{Noise-aware training via LiLAW}

Label imputation corrects false negatives where a post-assessment diagnosis conclusively implies a test was needed. It cannot resolve cases where the clinical indication is ambiguous: chest pain sometimes warrants an ECG and sometimes does not, so no imputation rule can adjudicate these encounters. Residual false negatives of this kind remain in both the original and imputed training sets. LiLAW (Lightweight Learnable Adaptive Weighting)~\cite{moturu_lilaw_2025} handles this residual noise at training time by learning to down-weight samples whose observed label is inconsistent with the model's predictions.

\paragraph{Sample difficulty characterization.}

Let $s_i = \mathrm{softmax}(f_\theta(x_i))$ be the model's output distribution for training sample $i$ with observed label $\tilde{y}_i$. LiLAW characterizes each sample by two quantities: $s_i[\tilde{y}_i]$, the predicted probability assigned to the observed label, and $\max(s_i)$, the model's peak class confidence. Their relationship defines four difficulty regimes:

\begin{itemize}
    \item \textit{Easy}: $s_i[\tilde{y}_i] = \max(s_i)$ and $\max(s_i)$ is high. The model agrees with the observed label confidently.
    \item \textit{Moderate}: $\max(s_i)$ is low regardless of agreement. The model is uncertain.
    \item \textit{Hard}: $s_i[\tilde{y}_i] < \max(s_i)$ and $\max(s_i)$ is high. The model confidently predicts a different class than the observed label — the signature of a likely mislabelled sample.
\end{itemize}

In our setting, hard samples correspond precisely to the false negatives that remain after imputation: encounters where the model assigns high probability to ``test needed'' but the training label records ``test not performed.'' These are the cases most likely to reflect external-provider tests that were never captured in the SickKids EHR.

\paragraph{Weight functions.}

LiLAW introduces three scalar meta-parameters, $\alpha$, $\beta$, and $\delta$, each governing a weight function over the $(s_i[\tilde{y}_i],\, \max(s_i))$ plane:

\begin{align}
    \mathcal{W}_\alpha &= \sigma\!\left(\alpha \cdot s_i[\tilde{y}_i] - \max(s_i)\right) \\
    \mathcal{W}_\beta  &= \sigma\!\left(-\left(\beta \cdot s_i[\tilde{y}_i] - \max(s_i)\right)\right) \\
    \mathcal{W}_\delta &= \exp\!\left(-\frac{\left(\delta \cdot s_i[\tilde{y}_i] - \max(s_i)\right)^2}{2}\right)
\end{align}

$\mathcal{W}_\alpha$ is a sigmoid that is high for easy samples (agreement, high confidence); $\mathcal{W}_\beta$ is an inverted sigmoid that is high for hard samples (disagreement, high confidence); $\mathcal{W}_\delta$ is a radial basis function centered on the moderate regime (low confidence either way). The total sample weight is $\mathcal{W} = \mathcal{W}_\alpha + \mathcal{W}_\beta + \mathcal{W}_\delta$, and the LiLAW loss is $\mathcal{L}_W = \mathcal{W} \cdot \mathcal{L}$. As $\alpha$, $\beta$, and $\delta$ are learned, the model adapts which difficulty regime to emphasise at each stage of training rather than applying a fixed curriculum.

\paragraph{Bilevel optimization.}

The meta-parameters are learned via bilevel optimization. Each training mini-batch alternates between two steps. In the inner step, $\alpha$, $\beta$, and $\delta$ are frozen and the model parameters $\theta$ are updated by gradient descent on the weighted training loss $\mathcal{L}_W$. In the outer step, $\theta$ is frozen and a validation mini-batch is drawn; $\alpha$, $\beta$, and $\delta$ are then updated by SGD on the LiLAW loss evaluated on that validation batch. The joint objective is:

\begin{align}
    \theta^* &= \arg\min_{\theta}\; \sum_{(x_i, \tilde{y}_i) \in \mathcal{D}_t} \mathcal{L}_{W_{\alpha^*,\beta^*,\delta^*}} \notag \\
    \text{s.t.}\quad \alpha^*, \beta^*, \delta^* &= \arg\min_{\alpha,\beta,\delta}\; \sum_{(x_j, \tilde{y}_j) \in \mathcal{D}_v} \mathcal{L}_{W_{\theta^*}}
\end{align}

Crucially, the validation set $\mathcal{D}_v$ does not need to be clean. Accuracy on a held-out noisy set is an unbiased estimator of accuracy under the noisy data distribution~\cite{moturu_lilaw_2025}, so LiLAW can steer training using the same validation partition used for early stopping. This property is essential for our setting, where a clean labelled subset of the EHR data is not available.

\paragraph{Implementation.}

LiLAW wraps the existing training loop without modifying the model architecture, adding only one forward and one backward pass on a validation mini-batch per training batch. Meta-parameters are initialised at $\alpha = 10.0$, $\beta = 2.0$, $\delta = 6.0$ and updated by SGD with learning rate $0.005$ and weight decay $10^{-4}$. The first epoch uses standard unweighted BCE loss as a warmup before LiLAW activates, allowing the model to develop an initial difficulty signal before meta-learning begins.

\subsection{Combined approach}

In the combined condition, LiLAW training is applied to the GraphRAG-imputed dataset. The two interventions target complementary failure modes. GraphRAG corrects the deterministic subset of false negatives, where a documented diagnosis clearly implies a test was needed. LiLAW handles the residual probabilistic uncertainty, down-weighting samples whose loss magnitude during training suggests misclassification. Imputation reduces the noise rate; LiLAW adapts to whatever noise remains.
