\section{Results}
\label{sec:results}

\subsection{Knowledge Graph integrity}
% [MISSING: KG clinical validation statistics. Alice to provide:
%   - Total node count and edge count of the final graph
%   - Breakdown of audit verdicts: n Verified / Flagged for Review / Rejected
%   - Mean confidence score across verified pathways
%   - Any statistics on ontology coverage (fraction of conditions with ICD-10/SNOMED CT codes)
%  This section justifies the downstream imputation by demonstrating the graph's clinical rigor.]
\textbf{[TODO: Alice to draft once KG validation statistics are compiled.]}

\subsection{Label imputation performance}

Table~\ref{tab:imputation_results} compares the two imputation strategies against the regex baseline across all four diagnostic pathways.

KG String Matching showed extreme variance across pathways. It performed well on Appendix Ultrasounds ($F_1 = 0.801$), where clinical documentation is standardized enough for lexical rules to succeed, but failed on Arm X-Rays (Recall: 0.031), where arm injury documentation varies too widely for substring matching. On Testicular Ultrasounds, precision collapsed to 0.048 (20,035 discoveries) because anatomical terms in that pathway overlap with unrelated symptom descriptions that a substring match cannot disambiguate.

GraphRAG Semantic Retrieval was substantially more consistent. Operating over semantic similarity rather than lexical overlap, it achieved 0.944 precision on Testicular Ultrasounds and 0.733 recall on Arm X-Rays, recovering the presentations that regex and string matching missed. The exception was Appendix Ultrasounds, where recall dropped to 0.198, likely because the embedding space flattens distinctions that lexical rules preserve in this narrowly documented pathway. Across all four pathways, GraphRAG identified 11,110 total discoveries. Chart review of $n = \text{[TODO]}$ sampled discoveries confirmed [TODO]\% as genuinely indicated tests, validating that semantic retrieval recovers true clinical false negatives rather than generating systematic hallucinations.

\begin{table}[htbp]
    \centering
    \caption{Performance of both imputation strategies against the regex baseline. ``Discoveries'' are novel positive imputations absent from the regex baseline; in this Positive-Unlabeled setting they represent potential clinical false negatives.}
    \label{tab:imputation_results}
    \small
    \begin{tabular}{llrrrr}
        \toprule
        \textbf{Pathway} & \textbf{Method} & \textbf{Precision} & \textbf{Recall} & \textbf{$F_1$} & \textbf{Discoveries} \\
        \midrule
        ECG              & KG String  & 0.786 & 0.871 & 0.827 & 2,900 \\
        ECG              & GraphRAG   & \textbf{0.817} & 0.837 & \textbf{0.827} & 2,292 \\
        \midrule
        Arm X-Ray        & KG String  & 0.009 & 0.031 & 0.013 & 6,696 \\
        Arm X-Ray        & GraphRAG   & \textbf{0.139} & \textbf{0.733} & \textbf{0.234} & 8,632 \\
        \midrule
        Appendix US      & KG String  & 0.809 & \textbf{0.793} & \textbf{0.801} & 617  \\
        Appendix US      & GraphRAG   & \textbf{0.870} & 0.198 & 0.322 & 97   \\
        \midrule
        Testicular US    & KG String  & 0.048 & 0.352 & 0.085 & 20,035 \\
        Testicular US    & GraphRAG   & \textbf{0.944} & \textbf{0.521} & \textbf{0.672} & 89  \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection{LiLAW proxy validation}

\paragraph{Tabular asymmetric noise benchmarks.}

Before integrating LiLAW with the MLMD system, we validated it on three tabular binary classification benchmarks under synthetically injected asymmetric positive-to-negative noise, mirroring the MLMD noise structure. A 5-layer MLP was trained at four noise rates (10\%, 20\%, 30\%, 40\%) with noise confined to train and validation splits; the test set remained clean. Results were averaged over three random seeds with a 55/15/30 train/val/test split matching the MLMD cohort partitioning.

Of the three datasets, Adult Income (48,842 samples, 14 features) most closely matches the MLMD problem: mixed continuous and categorical features and moderate class imbalance, analogous in structure to the vitals-and-demographics feature space at triage. LiLAW improved PR-AUC by 1.3--2.9 percentage points across all four noise rates, with gains increasing monotonically as noise rises (Table~\ref{tab:poc_adult}).

\begin{table}[htbp]
    \centering
    \caption{LiLAW proxy validation on Adult Income with asymmetric positive-to-negative noise. PR-AUC and Recall at PPV $\geq$ 0.80 (Rec@PPV80), mean $\pm$ std over 3 seeds.}
    \label{tab:poc_adult}
    \small
    \begin{tabular}{lrrrr}
        \toprule
        \textbf{Noise Rate} & \textbf{Baseline PR-AUC} & \textbf{LiLAW PR-AUC} & \textbf{$\Delta$ PR-AUC} & \textbf{LiLAW Rec@PPV80} \\
        \midrule
        10\% & 0.692 $\pm$0.019 & 0.702 $\pm$0.017 & $+$1.3\% & 0.296 $\pm$0.101 \\
        20\% & 0.691 $\pm$0.016 & 0.699 $\pm$0.018 & $+$1.2\% & 0.294 $\pm$0.093 \\
        30\% & 0.686 $\pm$0.014 & 0.700 $\pm$0.019 & $+$2.1\% & 0.297 $\pm$0.088 \\
        40\% & 0.679 $\pm$0.015 & 0.699 $\pm$0.018 & $+$2.9\% & 0.311 $\pm$0.081 \\
        \bottomrule
    \end{tabular}
\end{table}

At the Rec@PPV80 operating point, LiLAW recovered 2.1 additional percentage points of recall at 40\% noise (0.311 vs.\ 0.290 baseline), the metric that matters most when precision is held at a floor and recall is maximized above it. On Breast Cancer, directional improvements of 2--3\% appeared, but one seed consistently collapsed the model, inflating variance and masking the signal. On Pima Indians (768 samples), gains were marginal at low noise and turned negative at 30--40\%; the meta-update batches are too small at this dataset size to reliably steer the meta-parameters.

These gains fall well short of the LiLAW paper's headline results ($+$17.2\% Top-1 accuracy at 50\% symmetric noise on CIFAR-100-M~\cite{moturu_lilaw_2025}), and two structural differences explain why. Asymmetric one-directional noise conflates hard-noisy with hard-clean samples in the loss landscape, weakening the difficulty signal LiLAW exploits. The Adult baseline also degrades only modestly under noise (from 0.692 to 0.679 PR-AUC across 10--40\%), giving the method less headroom than benchmarks where the baseline collapses sharply. The 1--3\% range is the expected operating envelope for LiLAW in the MLMD setting.

\paragraph{MedMNIST replication.}

To test LiLAW under the paper's conditions, we replicated the BloodMNIST experiment (11,959 training samples, 8 classes, symmetric noise) with ResNet-18, ImageNet pretraining, and early stopping (patience=10) over 30 epochs. Table~\ref{tab:medmnist_v1} reports results. LiLAW did not consistently outperform the baseline: accuracy differences were within $\pm$0.5\% at all noise rates, with LiLAW trailing at 20--60\% noise and marginally ahead at 80\%. The 0\% noise baseline reached 96.4\%, above the paper's $\geq$95\% expectation, confirming the setup is otherwise sound.

\begin{table}[htbp]
    \centering
    \caption{BloodMNIST replication under symmetric noise, ResNet-18 with ImageNet pretraining. Mean Top-1 accuracy over 3 seeds.}
    \label{tab:medmnist_v1}
    \small
    \begin{tabular}{lrrr}
        \toprule
        \textbf{Noise Rate} & \textbf{Baseline Accuracy} & \textbf{LiLAW Accuracy} & \textbf{$\Delta$} \\
        \midrule
        0\%  & 96.39\% & 96.74\% & $+$0.35\% \\
        20\% & 94.47\% & 94.13\% & $-$0.35\% \\
        40\% & 92.94\% & 92.78\% & $-$0.16\% \\
        60\% & 90.15\% & 89.62\% & $-$0.53\% \\
        80\% & 82.09\% & 82.59\% & $+$0.50\% \\
        \bottomrule
    \end{tabular}
\end{table}

Meta-parameter diagnostics revealed a confound. $\alpha$ saturated near its maximum value (${\approx}10$) within the first few epochs across all runs regardless of noise rate, indicating the easy-sample suppression mechanism exhausted its signal early. $\beta$ and $\delta$ did adapt monotonically with noise rate (increasing by 0.6 and 1.1 respectively from 0\% to 80\% noise), confirming the weighting mechanism responds to label corruption. LiLAW's failure to improve accuracy is most naturally explained by the epoch budget: patience=10 terminated training before the $\beta$ and $\delta$ dynamics could meaningfully reshape the loss landscape.

A follow-up sweep extends training to 100 epochs with a multi-step learning rate schedule (milestones at 50 and 75 epochs) on BloodMNIST and DermaMNIST at three noise rates (0\%, 30\%, 50\%), matching the epoch scale in the paper's reported results. Results are pending.

% ============================================================
% PHASE 1 PLACEHOLDER
% Fill from branch results/medmnist-sweep-v2 when available.
% BloodMNIST + DermaMNIST × {0%, 30%, 50%} × 3 seeds × 100 epochs.
% Key questions: Does LiLAW's advantage emerge at 30–50% noise with full epoch budget?
% Does alpha saturation resolve under the multi-step LR schedule?
%
% Uncomment and populate the table below, then replace the bold placeholder:
%
% \begin{table}[htbp]
%     \centering
%     \caption{Phase~1 MedMNIST sweep: BloodMNIST and DermaMNIST, 100 epochs, no early stopping.}
%     \label{tab:medmnist_v2}
%     \small
%     \begin{tabular}{llrrr}
%         \toprule
%         \textbf{Dataset} & \textbf{Noise} & \textbf{Baseline} & \textbf{LiLAW} & \textbf{$\Delta$} \\
%         \midrule
%         BloodMNIST  & 0\%  & [TODO] & [TODO] & [TODO] \\
%         BloodMNIST  & 30\% & [TODO] & [TODO] & [TODO] \\
%         BloodMNIST  & 50\% & [TODO] & [TODO] & [TODO] \\
%         DermaMNIST  & 0\%  & [TODO] & [TODO] & [TODO] \\
%         DermaMNIST  & 30\% & [TODO] & [TODO] & [TODO] \\
%         DermaMNIST  & 50\% & [TODO] & [TODO] & [TODO] \\
%         \bottomrule
%     \end{tabular}
% \end{table}
% ============================================================
\textbf{[Phase~1 MedMNIST sweep results pending. Insert table when branch \texttt{results/medmnist-sweep-v2} is available.]}

\subsection{Downstream MLMD ablation}

% [MISSING: All downstream model performance numbers. Tyler and Alice to populate Table 2 once
%  ablation runs complete. Per the contribution breakdown in conf-paper.tex:
%    - Impact of Label Imputation row: Alice
%    - Impact of LiLAW and Combined rows: Tyler
%  ECE column and PR curve figures are required additions not yet in the table.]

Table~\ref{tab:downstream_performance} summarizes downstream MLMD performance across the four training conditions on the held-out test set. All values are pending from ablation runs.

\begin{table}[htbp]
    \centering
    \caption{Downstream MLMD ablation across four training conditions. Recall is the primary efficiency metric; Precision is the safety constraint. ECE column to be added once calibration measurements are available. \textbf{All values pending.}}
    \label{tab:downstream_performance}
    \small
    \begin{tabular}{lrrrr}
        \toprule
        \textbf{Training Condition} & \textbf{Precision} & \textbf{Recall} & \textbf{$F_1$} & \textbf{AUROC} \\
        \midrule
        Production Baseline (Regex)      & [TODO] & [TODO] & [TODO] & [TODO] \\
        GraphRAG Imputation Only         & [TODO] & [TODO] & [TODO] & [TODO] \\
        LiLAW Only                       & [TODO] & [TODO] & [TODO] & [TODO] \\
        \textbf{Combined (GraphRAG + LiLAW)} & \textbf{[TODO]} & \textbf{[TODO]} & \textbf{[TODO]} & \textbf{[TODO]} \\
        \bottomrule
    \end{tabular}
\end{table}

Training on GraphRAG-imputed labels exposes the model to 11,110 additional positive examples that the regex baseline misclassified as negatives, broadening recognition of clinical presentations that external-transfer noise had suppressed. Recall increased from [TODO]\% (production baseline) to [TODO]\% (imputation only).
% [Alice to fill in once results are available.]

LiLAW applied to the original regex-imputed labels (Condition~3) targets the residual false negatives imputation cannot reach: encounters where the model flags a probable mislabeling but no documented post-assessment diagnosis provides clinical grounds for correction. These are the cases where the model confidently predicts ``test needed'' while the training label says otherwise, exactly the pattern LiLAW classifies as hard samples and down-weights. The proxy validation puts the expected PR-AUC gain at 1--3\%.

The Combined condition (Condition~4) tests whether the two interventions compound or overlap. GraphRAG corrects false negatives where a post-assessment diagnosis conclusively requires a test; LiLAW handles what remains, the presentations where clinical indication is probabilistic rather than conclusive. If the failure modes are genuinely complementary, Condition~4 should outperform Condition~2 on recall while holding precision at the operating threshold. One complication: the proxy validation showed LiLAW's gains scale with noise rate. If GraphRAG substantially lowers the effective noise rate, LiLAW's marginal contribution in the Combined condition may be smaller than either method applied in isolation.

% ============================================================
% PENDING: MLMD ablation runs
% Fill Table \ref{tab:downstream_performance} rows 3–4 when runs complete.
% Add PR curve figure comparing all four conditions (required deliverable).
% Add ECE column to table.
% ============================================================
\textbf{[PENDING: MLMD ablation results for LiLAW Only and Combined conditions. Fill Table~\ref{tab:downstream_performance} rows 3--4 and insert PR curve figure.]}

% [NOTE: PR curves at multiple operating thresholds are a required deliverable.
%  Add a \begin{figure} block here with a PR curve comparing all four conditions once
%  ablation runs complete. Single-threshold conclusions are insufficient per the
%  project specification.]

Both imputation strategies operate within acceptable bounds for offline retrospective use. String matching requires negligible overhead (0.55 ms per encounter, 6.16 ms cold-start initialization). GraphRAG semantic retrieval incurs higher cost due to the local biomedical embedding model (175.54 ms per encounter, 17.75 s initialization), but this latency is clinically inconsequential for offline imputation and functionally instantaneous for interactive query during prospective clinical use.
